Building a continuous benchmarking ecosystem in bioinformatics

### 2024-10-31 letter_to_editor.tex
more changes

\begin{itemize}
    \item Dr Salvador Capella Gutierrez, \texttt{salvador.capella@bsc.es}, leader of the Spanish National Bioinformatics (INB) Coordination Node at the Barcelona Supercomputing Center (BSC).
    \item Dr Malte Luecken, \texttt{malte.luecken@helmholtz-muenchen.de}, group leader of the Computational Cellular Health Group, Helmholtz Munich.
\end{itemize}

>>>>

\begin{itemize}
    \item Dr Salvador Capella Gutierrez, \texttt{salvador.capella@bsc.es}, leader of the Spanish National Bioinformatics (INB) Coordination Node at the Barcelona Supercomputing Center (BSC).
    \item Dr Malte Luecken, \texttt{malte.luecken@helmholtz-muenchen.de}, group leader of the Computational Cellular Health Group, Helmholtz Munich.
    \item Prof Dr Carole Goble , \texttt{carole.goble@manchester.ac.uk}, full professor and co-leader of the Information Management Group, School of Computer Science in the University of Manchester.
    \item Prof Dr Johannes Koester, \texttt{johannes.koester@uni-due.de}, professor for Bioinformatics and Computational Oncology, Institute for AI in Medicine (IKIM), University Medicine Essen.
\end{itemize}
